% \cvsection{PERSONAL DETAILS}
% \smallskip
% \begin{itemize}
% \item Date of Birth : 26/08/1997
% %
% \item Nationality : INDIA
% %
% \item Languages : English(fluent), Hindi(native)
% %
% \item Interests : Cooking, Jogging, Anime and Psychological Science
% \end{itemize}



\cvsection{Projects}
\cvproject{Line Follower Using Image Processing [Completed]}
\begin{itemize}
\item Built using custom designed circuits, Arduino, raspberry pi and Logitech webcam.
\smallskip
\item Successfully completed under the supervision of professor Spoorthi Shekar.
\end{itemize}
\smallskip


\cvproject{Website to Post and Share Literature [Completed]}
\begin{itemize}
\item Website to demonstrate database management using MySql commands.
\smallskip
\item Programming languages used were PHP, HTML, MySql and Java Script.
\smallskip
\item Successfully completed under the supervision of professor Sucharitha Shetty.
\end{itemize}
\smallskip


\cvproject{4 Limb Robot [On Hold]}
\begin{itemize}
\item Creating relational understanding between sensors(including video and audio) and actuators for autonomous decisions and actions.
% \smallskip

\item Integration of distributed environment for collective learning and an option for cloud based processing.
\smallskip
\item \textit{On Hold} to integrate the computing module used in the below mentioned AR Glasses.
\end{itemize}
\smallskip

\cvproject{AR Glasses [in Progress]}
\begin{itemize}
% \item 3d printed aluminum and nylon casing for better thermal regulation and smaller form factor.
% \smallskip
\item ARM based processor used, for extracting features from user's environment and augmenting virtual elements within the said environment.
\item 3 ESP32-S2 processors used to capture image, detect eye location of the user and prepare a 3d view for the said user.
\item Creating a base for data collection to create a personalized user data-set and form an understanding of area of interest within the perceived environment for the user. 
\end{itemize}

\cvproject{Pocket Watch [Almost completed]}
\begin{itemize}
\item A sub project of the above mentioned AR Glasses for testing and understanding the hardware capabilities of the modules created.
% \smallskip
\end{itemize}
% \cvsection{References}
% \begin{itemize}
%     \item \underline{\normalsize Erdem Danaci}  \linebreak \textbf{Industry Business | Solution \linebreak Business Development Manager} \linebreak erdem.danaci@se.com
%     \item \underline{\normalsize Daniel Zulawski} \linebreak \textbf{Applications Design Expert} \linebreak Daniel.zulawski@se.com
% \end{itemize}

\hdashrule{\linewidth}{1pt}{1ex}

\begin{itemize}
    \item Nationality : Indian
    \item Languages : English(fluent), Hindi(native), Japanese(basic)
    \item Interests : Cooking, Jogging, Anime and Psychological Science
    \smallskip
\end{itemize}

 Please visit the website \href{https://fenrir-so.tech}{\large \it fenrir-so.tech} and \href{https://github.com/samarth-ar10}{\large \it github.com/samarth-ar10} for project 3d visualization and references.
    